\subsubsection{Name}

Inst -- Creation of instances

\subsubsection{Synopsys}

\begin{verbatim}
Inst ( model
     , name
     , param
     , map 
     )
\end{verbatim}

\subsubsection{Description}

Instantiation of an instance. The type of the instance is given by the \verb-model- parameter. The connexions are made thanks to the \verb-map- parameters.

\subsubsection{Parameters}

\begin{itemize}
    \item \verb-Model- : Name of the mastercell of the instance to create (mandatory argument)
    \item \verb-name- : Name of the instance (optional)\\
When this argument is not defined, the instance has a name created by default. This argument is usefull when one wants to create a layout as well. Indeed, the placement of the instances is much easier when the conceptor has chosen himself the name f the instances.</para>
    \item \verb-param- : Arguments of the mastercell (optional : only for mastercells which require it)
    \item \verb-map- : Connexions in order to make the netlist\\
\end{itemize}
\indent \verb-param- and \verb-map- are dictionnaries as shown in the example below.

\subsubsection{Example}

\begin{verbatim}
Inst ( 'DpgenAnd2'
     , param = { 'nbit' : 4
               }
     , map   = { 'i0'  : in0
               , 'i1'  : in1
               , 'q'   : out
               , 'vdd' : vdd
               , 'vss' : vss
               }
     )
\end{verbatim}
  
\subsubsection{Errors}
    
Some errors may occur :
\begin{itemize}
    \item \verb-Error in Inst : the model Model does not exist.-\\\verb-Check CRL_CATA_LIB.-\\Either one has made a mistake in the name of the model, either the environment variable is not correct.
    \item \verb-Error in Inst : port does not exist in model Model.-\\One port in map is not correct.
    \item \verb-Error in Inst : one input net is not dimensionned.-\\The size of the output nets is automatically calculated bus the input nets must be dimensionned before being connected.
\end{itemize}
         
\subsubsection{See Also}

\hyperref[ref]{\emph{Introduction}}{}{Introduction}{secintroduction}
